Orientation Control System: Enhancing Aerial Maneuvers for Quadruped Robots

### 2023-01-04 mdpi2022roscia.tex
all equations are numbered

\begin{equation*}

@@

\end{equation*}

@@

\subsection{Flywheels Control Law}
\label{subsec:control_law}
To derive a control law based on the robot base orientation, we make use of \eqref{eq:cons_ang_mom}, expressing all the contributions to the time derivative of total angular momentum with the respect to the base reference frame:
\begin{equation*}
\tensor[_b]{\bm{I}}{_f} \, \tensor[_b]{\dot{\bm{\omega}}}{_f} + \tensor[_b]{\bm{I}}{_r} \tensor[_b]{\dot{\bm{\omega}}}{_r} + \tensor[_b]{\bm{\omega}}{_r} \times \left( \tensor[_b]{\bm{I}}{_r} \tensor[_b]{\bm{\omega}}{_r}\right) = 0
\end{equation*}
From this expression, we can define the moment on the base caused by the acceleration of the flywheels, that can be used as a feedback torque $\bm{\tau}_{fb}$:
\begin{equation*}
\begin{split}
\bm{\tau}_{fb} &= \bm{I}_f \dot{\bm{\omega}}_f \\
&= - \tensor[_b]{\bm{I}}{_r} \dot{\bm{\omega}}_b - \tensor[_b]{\bm{\omega}}{_r} \times \left( \tensor[_b]{\bm{I}}{_r} \tensor[_b]{\bm{\omega}}{_r}\right)
\end{split}
\end{equation*}
We can use the \MF{proportional and derivative} action $\bm{K}_p \bm{e} + \bm{K}_d \dot{\bm{e}_r}$, where $\bm{K}_p$ and $\bm{K}_d$ are diagonal and positive-definite gain matrices for the error in attitude and angular velocity.
The orientation error $\bm{e} \in SO(3)$ needs the algebra of the special rotational group to be computed. To avoid singular configurations, we represent the orientation with quaternions.
The derivative error can be computed using $\dot{\bm{e}} = \tensor[_b]{\bm{\omega}}{_r^{des}} - \tensor[_b]{\bm{\omega}}{_r}$, in which $\tensor[_b]{\bm{\omega}}{_r^{des}}$ and $\tensor[_b]{\bm{\omega}}{_r}$ are, respectively, the desired and actual angular velocity of the base:
\begin{equation*}
\bm{\tau}_{fb} = - \tensor[_b]{\bm{I}}{_r} \left(\bm{K}_p \bm{e} + \bm{K}_d \dot{\bm{e}}\right) - \tensor[_b]{\bm{\omega}}{_r} \times \left( \tensor[_b]{\bm{I}}{_r} \tensor[_b]{\bm{\omega}}{_r}\right).
\end{equation*}
Projecting the moment $\bm{\tau}_{fb}$ onto the flywheel axes with $\bm{C}^T$, we obtain the control action $\bm{u}$
\begin{equation}
\label{eq:ctrl_law}
\bm{u} = \bm{C}^T \bm{\tau}_{fb}.
\end{equation}

>>>>

\MF{\begin{equation}

@@

\end{equation}}

@@

\subsection{Flywheels Control Law}
\label{subsec:control_law}
To derive a control law based on the robot base orientation, we make use of \eqref{eq:cons_ang_mom}, expressing all the contributions to the time derivative of total angular momentum with the respect to the base reference frame:
\MF{\begin{equation}
\tensor[_b]{\bm{I}}{_f} \, \tensor[_b]{\dot{\bm{\omega}}}{_f} + \tensor[_b]{\bm{I}}{_r} \tensor[_b]{\dot{\bm{\omega}}}{_r} + \tensor[_b]{\bm{\omega}}{_r} \times \left( \tensor[_b]{\bm{I}}{_r} \tensor[_b]{\bm{\omega}}{_r}\right) = 0
\end{equation}}
From this expression, we can define the moment on the base caused by the acceleration of the flywheels, that can be used as a feedback torque $\bm{\tau}_{fb}$:
\MF{\begin{equation}
\begin{split}
\bm{\tau}_{fb} &= \bm{I}_f \dot{\bm{\omega}}_f \\
&= - \tensor[_b]{\bm{I}}{_r} \dot{\bm{\omega}}_b - \tensor[_b]{\bm{\omega}}{_r} \times \left( \tensor[_b]{\bm{I}}{_r} \tensor[_b]{\bm{\omega}}{_r}\right)
\end{split}
\end{equation}}
We can use the \MF{proportional and derivative} action $\bm{K}_p \bm{e} + \bm{K}_d \dot{\bm{e}_r}$, where $\bm{K}_p$ and $\bm{K}_d$ are diagonal and positive-definite gain matrices for the error in attitude and angular velocity.
The orientation error $\bm{e} \in SO(3)$ needs the algebra of the special rotational group to be computed. To avoid singular configurations, we represent the orientation with quaternions.
The derivative error can be computed using $\dot{\bm{e}} = \tensor[_b]{\bm{\omega}}{_r^{des}} - \tensor[_b]{\bm{\omega}}{_r}$, in which $\tensor[_b]{\bm{\omega}}{_r^{des}}$ and $\tensor[_b]{\bm{\omega}}{_r}$ are, respectively, the desired and actual angular velocity of the base:
\MF{\begin{equation}
\bm{\tau}_{fb} = - \tensor[_b]{\bm{I}}{_r} \left(\bm{K}_p \bm{e} + \bm{K}_d \dot{\bm{e}}\right) - \tensor[_b]{\bm{\omega}}{_r} \times \left( \tensor[_b]{\bm{I}}{_r} \tensor[_b]{\bm{\omega}}{_r}\right).
\end{equation}}
Projecting the moment $\bm{\tau}_{fb}$ onto the flywheel axes with $\bm{C}^T$, we obtain the control action $\bm{u}$
\begin{equation}
\label{eq:ctrl_law}
\bm{u} = \bm{C}^T \bm{\tau}_{fb}.
\end{equation}
